An Oral History Project: Coke Studio and the Revitalization of Eastern Music

### 2022-04-20 paper.tex
partial progress on sufism

>>>>

  \section{A Reintroduction of Sufi Culture}

  There are three main branches in the religion of Islam. Sunni - the normative
  version of Islam practiced by the majority of the world. Shi'a - a smaller but
  not insignificant sect with minor differences in religious interpretation. And
  finally, there is Sufi Islam. Although technically Sufi Islam is not
  considered by some to be a separate branch of Islam, many of their practices
  are not found in normative Islam and thus, for the purposes of this paper they
  will be considered a different "branch" or "sect".

  Sufi Islam is commonly defined "Islamic Mysticism" and tends to emphasize the 
  spiritual aspects of the religion more so than the legalistic, or worldy
  elemnts. For most orientalists, the religion is thus seen as the more 
  moderate, "peaceful" interpretation of islam \autocite{beg2020fizzy}. This of
  course incorrectly implies that traditional mainstream islam is oppressive,
  but nevertheless the perception of Westerners ironically have a large
  influence on what local Pakistanis wish to express their culture. As a
  consequence, embracing the Sufi genre of music - the Qawwali - is a nice
  middle ground in appeasing to a moderate image of Islam while simultaneously 
  appealing to the more religiously inclined in the nation who are skeptical of
  the value of music in society \autocite{beg2020fizzy}.

  The Qawwali is a musical manifestation of Sufism. It's a piece of religious music 
  that tends to be 10-20 minutes long, but can range up to an hour and is typically 
  based on religious poetry. The piece starts out slowly, with a couple words chanted
  in the begining, but quickly accelerates to a climax.
